%-------------------------
% Resume in Latex
% NAME: AARYA MOURYA 
% DATE: 26-11-24
% NOTE: ROBOTICS AND COMPUTER VISION RELATED INTERNSHIPS AND JOBS RELATED RESUME
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape AARYA MOURYA} \\ \vspace{5pt}
    
    \small 
    \raisebox{-0.1\height}\faPhone\ +91 9324229472 ~ 
    \href{mailto:aarya.a.mourya@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{aarya.a.mourya@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/aarya-mourya-444051566612094454/}{\raisebox{-0.2\height}\faLinkedin\ \underline{Linkedin: aarya-mourya}} ~
    \href{https://github.com/Aarya-Mourya}{\raisebox{-0.2\height}\faGithub\ \underline{Github: Aarya-Mourya}} ~
    \href{https://aarya-mourya.github.io/aarya-mourya-portfolio.io/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://slrtce.in/}{Shree L.R. Tiwari College of Engineering (SLRTCE)}, Mumbai}{Dec 2021 -- May 2025}
      {Bachelor of Engineering - Electronics and Computer Science}{7.08 CGPA}
    
    \resumeSubheading
      {\href{https://svpjc.in/}{SVP Junior College}, Maharashtra}{June 2020 -- May 2021}
      {Higher Secondary Certificate (HSC)}{71.17\%}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C++, MATLAB, Bash, \LaTeX} \\
     \textbf{Libraries/Frameworks}{: ROS2, Rviz2, Gazebo, MoveIt!, OpenCV, Scikit-Learn, NumPy, Matplotlib} \\
     \textbf{Environment/Tools:}{ Linux, Git, GitHub, Fusion-360, AWS Cloud Foundation, Canva, MS Office (Word, Excel, PPT)} \\
     \textbf{Soft Skills:}{ Leadership, Public Speaking, Public Relations, Team Work} \\
     \textbf{Languages:}{ English, Hindi} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.womeninrobotics.org/}{Women in Robotics - Non-Profit Organization}}{Sep 2024 -- Present}
  {Volunteer Member}{Remote}
  \resumeItemListStart
    \resumeItem{Conducted design sessions and workshops to empower women in the robotics industry.}
    \resumeItem{Networked with professionals and collaborators to enhance outreach and community engagement.}
  \resumeItemListEnd

  \resumeSubheading
  {\href{https://www.linkedin.com/school/shree-l-r-tiwari-college-of-engineering-thane/}{Department of Computer Engineering - SLRTCE}}{June 2024 -- July 2024}
  {Linux Internship Trainee - Mentored by {\href{https://slrtce.in/ia-profile-rajesh-gaikwad}{\textbf{Prof. Rajesh Gaikwad}}}}{Mumbai (On-site)}
  \resumeItemListStart
    \resumeItem{Administered Linux systems, managing users, file permissions, and networking tasks.}
    \resumeItem{Enhanced system security through IPtables firewalls and SSH key authentication.}
  \resumeItemListEnd

\resumeSubheading
  {\href{https://www.theinnovationstory.com/}{The Innovation Story} - STEM Innovators }{Oct 2023 -- Mar 2024}
  {Internship}{Dadar (Hybrid)}
  \resumeItemListStart
    \resumeItem{Created designs and collaborated on engaging visuals for branding and marketing.}
    \resumeItem{Designed T-shirts for the FIRST Robotics Competition.}
  \resumeItemListEnd
  
\resumeSubheading
  {\href{https://www.linkedin.com/school/shree-l-r-tiwari-college-of-engineering-thane/}{Department of Computer Engineering - SLRTCE}}{Mar 2023 -- Apr 2023}
  {Cybersecurity Internship Trainee - Mentored by {\href{https://slrtce.in/ia-profile-rajesh-gaikwad}{\textbf{Prof. Rajesh Gaikwad.}}}}{Mumbai (On-site)}
  \resumeItemListStart
    \resumeItem{Managed system administration tasks, automated operations with Bash scripts, and configured IPtables firewalls.}
    \resumeItem{Secured systems with SSH key-based authentication.}
  \resumeItemListEnd

\resumeSubheading
  {\href{https://ecell-slrtce.github.io/}{E-Cell - SLRTCE}}{Jul 2022 -- Jun 2023}
  {Graphic Lead \& Graphic Design Coordinator} {Mumbai (On-site)}
  \resumeItemListStart
    \resumeItem{Coordinated graphic design projects and led event preparations for entrepreneurship programs.}
    \resumeItem{Played a key role in E-Summit 2023, supporting competitions and collaborating with teammates.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Intelligent AMR with Integrated Visual and Sensor-Based Navigation} $|$ \emph{July, 2024 - Present}}
          {\href{}{(GitHub Link)}}
          \resumeItemListStart
            \resumeItem{Designed a 2-Wheel Differential Drive AMR with Arduino UNO and Raspberry Pi, integrating sensors (LiDAR, IMU, Encoders, Camera) for advanced perception and navigation.}
\resumeItem{\textbf{Key functionalities of the robot:} Teleoperation, Autonomous Navigation, SLAM, Object Detection, Classification, Path Planning, Obstacle Avoidance, Gesture Control.}
\resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {\textbf{Autism Spectrum Disorder (ASD) Prediction Using Machine Learning} $|$ \emph{June, 2024 - July, 2024}}
          {\href{https://github.com/Aarya-Mourya/Autism-Prediction-using-Machine-Learning-Python}{(GitHub Link)}}
    \resumeItemListStart
    \resumeItem{Developed a machine learning model for predicting ASD, utilizing data from surveys and applying Random Forest Classifier.}
    \resumeItem{Evaluated model performance using F1 score, precision, recall, and accuracy, and created a GUI for result visualization.}
        \resumeItemListEnd
          \vspace{-13pt}

    \resumeSubHeadingListEnd

      \resumeProjectHeading
  {\textbf{Sign Language Recognition for Deaf and Mute People} $|$ \emph{April, 2023 - July, 2024}}
  {\href{https://github.com/Aarya-Mourya/Sign-Language-Recognition-For-Mute-And-Deaf}{(GitHub Link)}}
  \resumeItemListStart
\resumeItem{Developed an ASL recognition system using Linux, Python, OpenCV, and Google's Mediapipe library for hand gesture detection, achieving high accuracy with a Random Forest Classifier for gesture recognition.}
\resumeItem{Using Matplotlib for data visualization and NumPy for efficient numerical computations, ensuring fast real-time processing for the recognition system.}
  \resumeItemListEnd 
  \vspace{-13pt}
  
  \resumeProjectHeading
  {\textbf{Autonomous Maze Solving Robot} $|$ \emph{August, 2022 - April, 2023}}
  {\href{https://github.com/Aarya-Mourya/Autonomous-Maze-Solving-Robot}{(GitHub Link)}}
  \resumeItemListStart
\resumeItem{Built a 2-Wheel Differential Drive autonomous robot using Arduino UNO and sensors to navigate mazes with collision - avoidance algorithms and servo motor control.}
\resumeItem{Designed CAD models for the robot and maze using Shapr3D, integrated hardware components including an HC-SR04 ultrasonic sensor, and created detailed electronic schematics with TinkerCAD Circuits.}
  \resumeItemListEnd 
\resumeSubHeadingListEnd
\vspace{-5pt}
\end{document}
